Efficient, Robust and Exact Boolean Operations on N Triangular Mesh Primitives

### 2016-10-04 summary.tex
10.5

\IEEEtitleabstractindextext{
\begin{abstract}
  Constructive solid geometry is widely used for computer aided design and manufacturing. However, boolean operations, which compute the boundary representation of constructive solid geometry, have been suffered from robustness and efficiency problem for more than three decades. In this paper, we propose a fast and exact boolean operation approach which is theoretically robust for valid triangle mesh inputs. This is done by introducing plane-based geometry into boolean operations and strictly follow the principle of no constructions during processing. Different from previous BSP-based method, our method works on halfedge, with only one-time conversion to the plane representation in intersection areas, instead of a series of complex conversions between different representations. Also, by using geometry connectivity and space neighboring information, our method reuse the computation iteratively, saving much computation time. Comparison experiments with state-of-the-art techniques show that our method is unconditionally exact and robust, while is competitively efficient with non-robust methods and much faster than exact, robust ones.
\end{abstract}

@@

In general, there are two major types of boolean algorithms according to how they deal with intersection between primitive meshes. Approximate methods redicretize the intersection areas, fit vertices approximatively and rearrange topology. On the other hand, exact method do not change vertex positions, retain as many input elements  (e.g., faces, vertices and topology) as possible. In many applications, exact methods are preferred for their accuracy. Also, using exact methods, the clear mapping between the surface of input and output meshes makes it easier for the inheritance of information like face colors and materials. However, for exact boolean operation methods, there is always a bargain between robustness and efficiency. Recent exact boolean operation methods try to find faster ways to compute boundaries of CSG. However, for robustness, the answers are often exact arithmetic \cite{barki2015exact,zhou2016mesh} or trivial workarounds, like setting a tolerance \cite{feito2013fast,segal1990using} or rotating the primitive with small angles to avoid coplanar cases \cite{douze2015quickcsg}. However, none of the solution is good enough. While exact-arithmetic based methods are significantly slower, workarounds are often case dependent and not reliable for complex CSGs.

We develop an unconditionally robust and exact boolean operation method for triangle meshes without using exact arithmetic. The robustness of our method is based on the observations by Sugihara and Iri \cite{sugihara1990solid} that boolean operations can be performed requiring geometry constructions if representations are based on planes and not vertices. This idea of using plane-based representation (P-rep) has been developed by Berstein and Fussell \cite{bernstein2009fast} by combining it with binary search partition (BSP) techniques \cite{naylor1990merging,thibault1987set}. Later, Campen et. al. \cite{campen2010exact} improved the method using octrees to resolve intersections locally, avoiding inefficient large BSP tree construction. Despite of that, Campen et. al.'s method still suffers from performance problem because of the complex conversions among B-reps, P-reps and BSP representations. Also, the incoherence between BSP representation, where boolean operations actually happens, and B-reps, which are input and output meshes, requires extra steps to connect the reconstructed intersection areas with the untouched meshes, leading to extra computation burden and complex topology.

We adopt plane-based techniques and strictly follow the principle of no geometry construction, yet develop a very different framework based on halfedges, requiring only one-time conversion to the plane representation in intersection areas. Since the geometry connectivity is stored in halfedge, it allow us to take advantage of geometry connectivity for classification acceleration \cite{feito2013fast,ogayar2015deferred,updegrove2016boolean}, which is hard to for a BSP-based method. In addition, our method can perform boolean operations with more than two primitives in one call, instead of recursively doing binary boolean operations. In this way, extra complexity is introduced. But we can save much computation time by avoiding repetitive computation. The major difficulty of applying P-rep on halfedge is by the incoherence between the two representations. Halfedge is a vertex-based representation. Many geometry operations (e.g., coordinates projection and compute the barycenter coordinate of triangle) available on halfedge can be very complex and thus inefficient under P-rep. On the other hand, we have to compute under P-rep for exactness and robustness. Therefore, we manage to limit our computation of boolean operations to several basic plane-based predicates. The experiment shows that our method is much faster than Campen et. al.'s method, while only about two to three times slower than the state-of-art non-robust method \cite{douze2015quickcsg}.

>>>>

\IEEEtitleabstractindextext{
\begin{abstract}
  Constructive solid geometry (CSG) is widely used for computer aided design and manufacturing. However, boolean operations, which compute the boundary representation of CSG, have been suffered from robustness and efficiency problem for more than three decades. In this paper, we propose a fast and exact boolean operation approach which is theoretically robust for regular meshes. This is done by introducing plane-based geometry into boolean operations and strictly follow the principle of no geometry constructions during processing. Different from previous BSP-based methods, our method is with only one-time conversion to the plane representation in intersection areas, instead of a series of complex conversions between different representations. Also, by using geometry connectivity and space neighboring information, our method reuse the computation iteratively, saving much computation time. Comparison experiments with state-of-the-art techniques show that our method is unconditionally exact and robust, while is competitively efficient with non-robust methods and much faster than the robust ones.
\end{abstract}

@@

In general, there are two major types of boolean algorithms according to how they deal with intersection between primitive meshes. Approximate methods redicretize the intersection areas, fit vertices approximatively and rearrange topology. On the other hand, exact method do not change vertex positions, retain as many input elements  (e.g., faces, vertices and topology) as possible. In many applications, exact methods are preferred for their accuracy. Also, using exact methods, the clear mapping between the surface of input and output meshes makes it easier for the inheritance of information like face colors and materials. However, for exact boolean operation methods, there is always a bargain between robustness and efficiency. Recent exact boolean operation methods try to find faster ways to compute boundaries of CSG. However, for robustness, the answers are often exact arithmetic \cite{barki2015exact,zhou2016mesh} or trivial workarounds, like setting a tolerance \cite{feito2013fast,segal1990using} or rotating the primitive with small angles to avoid coplanar cases \cite{douze2015quickcsg}. However, none of the solution is good enough. While methods using exact arithmetic are significantly slower, workarounds are often case dependent and not reliable for complex CSGs.

We develop an unconditionally robust and exact boolean operation method for triangle meshes without using exact arithmetic. The robustness of our method is based on the observations by Sugihara and Iri \cite{sugihara1990solid} that boolean operations can be performed requiring geometry constructions if representations are based on planes. This idea of using plane-based representation (P-rep) has been developed by Berstein and Fussell \cite{bernstein2009fast} by combining it with binary search partition (BSP) techniques \cite{naylor1990merging,thibault1987set}. Later, Campen et. al. \cite{campen2010exact} improved the method using octrees to resolve intersections locally, avoiding inefficient large BSP tree construction. Despite of that, Campen et. al.'s method still suffers from performance problem because of the complex conversions among B-reps, P-reps and BSP representations. Also, the incoherence between BSP representation, where boolean operations actually happens, and B-reps, which are input and output meshes, requires extra steps to connect the reconstructed intersection areas with the untouched meshes, leading to extra computation burden and complex topology.

We develop a boolean operation method based on vertex-based representation of mesh (e.g., halfedge) and embed plane-based techniques into it, requiring only one-time conversion to the plane representation in intersection areas. It allows us to take advantage of geometry connectivity for classification acceleration \cite{feito2013fast,ogayar2015deferred,updegrove2016boolean}, which is hard for BSP-based methods. In addition, our method can perform boolean operations with more than two primitives in one call, instead of recursively doing incremental boolean operations. Despite of extra complexity, non-incremental boolean operation may save much computation time by avoiding repetitive computation. The major difficulty of embed P-rep on vertex-based representation is by the incoherence between the two representations. Many geometry operations (e.g., coordinates projection and compute the barycenter coordinate of triangle) available on vertex-based representations can be very complex and thus inefficient under P-rep. On the other hand, we have to compute all under P-rep for exactness and robustness. Therefore, we manage to limit our computation of boolean operations to several basic plane-based geometry predicates. The experiment shows that our method is much faster than exact, robust methods, while only about two to three times slower than the state-of-art non-robust method \cite{douze2015quickcsg}.
